Measuring Interaction Design\\ Measuring Interaction before developing prototypes\\ Measuring Interaction Graphs

### 2015-09-11 paper.tex
details

We present an approach that allows a designer to quickly 
\begin{inparaenum}[(a)]
\item understand how supportive an application is with respect to  user efficiency;
\item understand how prone the application is to user navigation
  errors;
\item understand how recoverable the application is from those errors;
\item support task analysis and task / scenario design;
%\item support interaction design (IxD) in terms of consistency, error-proneness, and recovery premature commitment;
\end{inparaenum}.  
%
Our approach further allows different designs to be
objectively compared to support designers in evaluating interaction
sequences. To explain our work we present a case study comparing four
different web mail front ends. We have chosen this domain because it
is very well understood by readers and yet those trivial questions
lead to non trivial results.

The approach is based on UML state-chart models of the user interfaces
which are automatically processed to produce \emph{interaction
  graphs}. These are then used to unfold \emph{execution traces} that
are dependent on the specific usage scenarios being considered in the
analysis. On traces several graph-theoretic computations can be
performed to produce a dashboard of different results that provide the
answers. Except for development of models and specification of the
desired scenarios, the other steps are totally automatic; models of a
design could be developed in a matter of a couple of hours.

>>>>

We present an approach that allows a designer to quickly 
\begin{inparaenum}[(a)]
\item understand how supportive an application is with respect to  user efficiency;
\item understand how prone the application is to user navigation
  errors;
\item understand how recoverable the application is from those errors;
\item support task analysis and task / scenario design.
%\item support interaction design (IxD) in terms of consistency, error-proneness, and recovery premature commitment;
\end{inparaenum}
%
Our approach further allows different designs to be objectively
compared to support designers in evaluating interaction sequences. To
explain our work we present (\S~\nameref{sec:casestudy}) a case study
comparing four different web mail front ends. We have chosen this
domain because it is very well understood by readers and yet those
trivial questions lead to non trivial results.

The approach is based on UML state-chart models of the user interfaces
which are automatically processed to produce \emph{interaction
  graphs}. These are then used to unfold \emph{execution traces} that
are dependent on the specific usage scenarios being considered in the
analysis (\S~\nameref{sec:traces}). On traces several graph-theoretic
computations can be performed to produce a dashboard of different
results that provide the answers. Except for development of models and
specification of the desired scenarios, the other steps are totally
automatic; models of a design could be developed in a matter of a
couple of hours.
